{\bf Kernel Methods and SVMs} \\ {\large A convex optimization point of view}

### 2016-06-10 coproject/report_tallec_lederrey.tex
UPD: Report compiled

\setlength{\textheight}{235mm}
\setlength{\topmargin}{-1.2cm} % pour centrer la page verticalement
%\setlength{\footskip}{5mm}
\setlength{\textwidth}{15cm}
\setlength{\oddsidemargin}{0.56cm}
\setlength{\evensidemargin}{0.56cm}
\setlength{\parindent}{0cm}

@@

The purpose of this script was to train SVMs on 60000 images with their
labels. And then, test the model on 10000 images. We could finally compare the
predicted labels against the real labels. In order to test the SVM method, we
trained the algorithm with different kernel functions. As SVMs naturally perform
binary classification, and not $n$-ary classification, one-vs-all classification
was used (that is we train the model n-times, once on each digit).
\begin{itemize}
\item Linear kernel: $K(x_i,x_j) = \langle x_i, x_j \rangle$
\item Polynomial kernel: $K(x_i,x_j) = (\gamma \langle x_i, x_j \rangle + r)^p$, $\gamma$ is a parameter that needs to be found and we decided to keep $r=0$ and we used $p=4$.
\item RBF kernel:  $K(x_i,x_j) = \exp(-\gamma|x_i-x_j|^2)$, $\gamma$ is a parameter that needs to be found.
\end{itemize}

@@

\bibitem{paper} Kim, Seung-Jean, et al. "Learning the kernel via convex optimization." {\it Acoustics, Speech and Signal Processing, 2008. ICASSP 2008. IEEE International Conference on.} IEEE, 2008.

>>>>

\setlength{\textheight}{240mm}
\setlength{\topmargin}{-1.5cm} % pour centrer la page verticalement
%\setlength{\footskip}{5mm}
\setlength{\textwidth}{15cm}
\setlength{\oddsidemargin}{0.56cm}
\setlength{\evensidemargin}{0.56cm}
\setlength{\parindent}{0cm}

@@

The purpose of this script was to train SVMs on 60000 images with their
labels. And then, test the model on 10000 images. We could finally compare the
predicted labels against the real labels. In order to test the SVM method, we
trained the algorithm with different kernel functions. As SVMs naturally perform
binary classification, and not $n$-ary classification, one-vs-all classification
was used (that is we train the model n-times, once on each digit).
\newpage
\begin{itemize}
\item Linear kernel: $K(x_i,x_j) = \langle x_i, x_j \rangle$
\item Polynomial kernel: $K(x_i,x_j) = (\gamma \langle x_i, x_j \rangle + r)^p$, $\gamma$ is a parameter that needs to be found and we decided to keep $r=0$ and we used $p=4$.
\item RBF kernel:  $K(x_i,x_j) = \exp(-\gamma|x_i-x_j|^2)$, $\gamma$ is a parameter that needs to be found.
\end{itemize}

@@

\bibitem{paper} Kim, Seung-Jean, et al. "Learning the kernel via convex optimization." {\it Acoustics, Speech and Signal Processing, ICASSP.} IEEE, 2008.
